---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Here are some plots for our website. 

Today, we're making interactive plots in plotly. We'll make examples using the Instacart data from the p8105.datasets package. 

```{r, results='hide'}
library(tidyverse)
library(p8105.datasets)
library(dplyr)
library(flexdashboard)
knitr::opts_chunk$set(echo = TRUE)
library(plotly)

data("Instacart")

janitor::clean_names(instacart)

```

### Initial data cleaning/subsetting.


I decided to keep three variables: `order_hour_of_day`, `department`, `days_since_prior_order`. 

```{r}
instacart_ = 
  instacart |> 
  select(order_hour_of_day, department, days_since_prior_order)

```


Use plotly to make a histogram plot, a box plot, and a bar graph. First, we are making a histogram to see the distribution of orders by hour. The most orders were placed at 2pm.  

### Histogram

```{r}

instacart_ |> 
  plot_ly( 
    x = ~order_hour_of_day, type = "histogram", 
    marker = list(color = "pink",line = list(color = "grey",width = 2))) |>
  layout(title = "Hours At Which Orders Were Placed",
         xaxis = list(title = "Order Hours"),
         yaxis = list(title = "Frequency"))


```


### Boxplot

Next up - We are making a box plot. We are looking at department by the number of days since prior order. 
```{r, warning=FALSE}
instacart |> 
  plot_ly(
    x = ~department, y = ~days_since_prior_order, color = ~department,
    type = "box")
```

### Bar Chart

Let's do a bar chart with number of orders by department. Produce has the highest number of orders. 
```{r, warning=FALSE}
instacart |> 
  count(department) |> 
  mutate(department = fct_reorder(department, n)) |> 
  plot_ly(
    x = ~ department, y = ~n, color = ~department,
    type = "bar")
```